Predicted cardiovascular risk and blood pressure for Americans with diabetes, chronic kidney disease, and \u226565 years of age

### 2020-09-18 doc/ACCAHA_BP_groups.Rmd
PM comments and gfr fix

Byron C. Jaeger^1^, Shakia T. Hardy^2^, Paul Muntner^2^, and Paul Whelton^3^

@@

# INTRODUCTION

_To be written in next draft_

@@

The current analysis was restricted to adults aged 40 to 79 years of age who complete the NHANES interview and examination (n = `r n_age_40_to_79`). Participants with age <40 or >79 years of age were not included because the Pooled Cohort risk equations are not recommended in these age ranges.[@goff20142013] Participants who did not have three SBP and DBP measurements (n = `r n_bp_too_low`) and those who were missing information on age, race, sex, total and high-density lipoprotein cholesterol, smoking status, diabetes, or CKD status (n = `r n_missing_pcr`) were excluded. After these exclusions, over the `r as.english(length(exams))` NHANES cycles, a total of `r n_final` survey participants were included in the analysis (`r refer_to('fig_include_exclude')`).

@@

Data were collected during an in-home interview and a study visit completed at a mobile examination center. Standardized questionnaires were used to assess participants’ age, sex, race/ethnicity, smoking habits, medical history and use of antihypertensive medication, oral glucose lowering medication and insulin. Medical history included questions about whether the participant had been told by a doctor or other health professional that they have had a heart attack, coronary heart disease stroke, or heart failure. Blood and urine samples were collected during the medical examination. Of relevance to the current analysis, serum creatinine, serum glucose and glycated hemoglobin (HbA1c) were measured. Diabetes was defined by fasting serum glucose ≥`r gluc_cutpoint_fasted` mg/dL, non-fasting glucose ≥`r gluc_cutpoint_fed` mg/dL, HbA1c ≥`r hba1c_cutpoint`%, or self-reported use of insulin or oral glucose lowering medication. Estimated glomerular filtration rate was calculated using the Chronic Kidney Disease Epidemiology Collaboration equation.[@levey2009new] Urinary albumin and creatinine levels were measured and used to calculate the albumin-to-creatinine ratio (ACR). CKD was defined by an estimated glomerular filtration rate <`r egfr_cutpoint` ml/min/1.73m^2^ or an ACR ≥`r acr_cutpoint` mg/dL. Ten-year predicted risk for ASCVD was calculated using the pooled cohort risk equations for participants without a history of CVD.[@goff20142013] Participants with a history of CVD were presumed to have 10-year risk for ASCVD ≥10%.

@@

Participants not taking antihypertensive medication were grouped into four non-overlapping categories based on the 2017 ACC/AHA BP guideline: Normal BP (SBP <120 mm Hg and DBP <80 mm Hg), elevated BP (SBP between 120 and 129 mm Hg and DBP <80 mm Hg), stage 1 hypertension (SBP between 130 and 139 mm Hg and/or DBP between 80 and 89 mm Hg with SBP <140 mm Hg and DBP <90 mm Hg), stage 2 hypertension (SBP ≥140 mm Hg or DBP ≥90 mm Hg). Participants taking antihypertensive medication were placed in a fifth group.

@@

Analyses were conducted for the overall population and among participants with diabetes, CKD, ≥65 years of age, and for those with any of these three conditions, separately. Participant characteristics were summarized as mean with their standard error and percentage for continuous and categorical variables, respectively. The percentage of US adults in each of the five BP categories was computed. The median 10-year predicted risk for ASCVD and the proportion with a predicted risk ≥10% was computed for participants in each of the BP categories. To assess the extent to which participants with a 10-year predicted ASCVD risk <10% were close to the threshold, the proportion of participants in this subgroup with predicted risk of 0% to <2.5%, 2.5% to <5.0%, 5.0% to <7.5%, and 7.5% to <10% was estimated. The probability of having a 10-year predicted ASCVD risk ≥10% was estimated for each year of age from 40 to 79 years using logistic regression. The above analyses were repeated among participants with stage 1 hypertension.

@@

NHANES sampling weights, which were calculated as the inverse probability of being selected for the survey, were used in all calculations to obtain US nationally representative estimates. The survey design of NHANES was also taken into account. Data analysis was conducted using `r version$version.string`. P-values were two-sided.

@@

Among US adults who were 40 to 79 years of age in `r min(exams)`-`r max(exams)+1`, the estimated prevalence (95% confidence interval [CI]) of diabetes and CKD was `r inline$prevDiabetesOverall` and `r inline$prevCkdOverall`, respectively, and `r inline$prevAge65Overall` were estimated to be ≥65 years of age (`r refer_to('tab_characteristics')`). Overall, an estimated `r inline$prevS1hOverall` of US adults who were 40 to 79 years of age had stage 1 hypertension (`r refer_to('tab_bpdist')`). Among those with diabetes, CKD, and age ≥65 years, the estimated prevalence (95% CI) of stage 1 hypertension was `r inline$prevS1hDiabetes`, `r inline$prevS1hCkd`, and `r inline$prevS1hAge65`, respectively. Characteristics of US adults 40 to 79 years of age with stage 1 hypertension, overall, and with diabetes, CKD and age ≥65 years are presented in Table S1

@@

Among US adults without a history of CVD, the estimated median (25th, 75th percentiles) 10-year predicted risk for ASCVD was `r inline$medianPcrOverall` in the overall population and `r inline$medianPcrDiabetes`, `r inline$medianPcrCkd`, and `r inline$medianPcrAge65` among those with diabetes, CKD, and age ≥65 years, respectively (`r refer_to('tab_risk_overall')`; top panel). Among US adults with stage 1 hypertension and no history of CVD, the estimated median (25th, 75th percentiles) 10-year predicted risk for ASCVD was `r inline$medianPcrS1hOverall`. Within this subgroup of adults with stage 1 hypertension, those with diabetes and CKD had median (25th, 75th percentiles) predicted risks of of `r inline$medianPcrS1hDiabetes` and `r inline$medianPcrS1hCkd`, respectively, while adults aged ≥65 years had a median (25th, 75th percentiles) predicted risk of `r inline$medianPcrS1hAge65`. Among all US adults with stage 1 hypertension, an estimated `r inline$prevHighRiskS1hDiabetes` of those with diabetes, `r inline$prevHighRiskS1hCkd` of those with CKD and `r inline$prevHighRiskS1hAge65` who were ≥65 years of age had a 10-year predicted risk for ASCVD ≥10% or a history of CVD (`r refer_to('tab_risk_overall')`; bottom panel).

@@

Among US adults with 10-year predicted risk for ASCVD <10% and no history of CVD, an estimated `r inline$propLowRiskOverall` had a 10-year predicted ASCVD risk <5% (`r refer_to('fig_hist_ovrl')`). Also, among those with 10-year predicted risk for ASCVD <10% and no history of CVD, `r inline$propLowRiskDiabetes`, `r inline$propLowRiskCkd`, and `r inline$propLowRiskAge65` of those with diabetes, CKD and age ≥65 years had a 10-year predicted ASCVD risk <5%. Among US adults with predicted risk <10% and stage 1 hypertension, `r inline$propLowRiskS1hDiabetes` of those with diabetes, `r inline$propLowRiskS1hCkd` of those with CKD, and `r inline$propLowRiskS1hAge65` of those with ≥65 years of age had a 10-year predicted ASCVD risk <5% (`r refer_to('fig_hist_stg1')`).

@@

The estimated probability of having a 10-year predicted ASCVD risk ≥10% or a history of CVD increased with older age and the minimum age where estimated probability was ≥50% was `r inline$ageHighRiskOvrlNoComorb` years for US adults without diabetes or CKD (`r refer_to('fig_risk_ovrl')`). For US adults with diabetes and with CKD, the age when estimated probability was ≥50% for having a 10-year predicted ASCVD risk ≥10% or a history of CVD was `r inline$ageHighRiskOvrlDiabetes` and `r inline$ageHighRiskOvrlCkd` years, respectively. Among US adults with stage 1 hypertension, the minimum age where estimated probability of having a 10-year predicted ASCVD risk ≥10% or history of CVD exceeded 50% was `r inline$ageHighRiskS1hNoComorb`, `r inline$ageHighRiskS1hDiabetes`, and `r inline$ageHighRiskS1hCkd` years for US adults without diabetes or CKD, with diabetes, and with CKD, respectively (`r refer_to('fig_risk_stg1')`). Since the median 10-year predicted risk for ASCVD was >10% among adults ≥65 years, a minimal age was not determined for this group.

@@

In the current study, the distribution of 10-year predicted risk for ASCVD was investigated among US adults aged 40 to 79 years in `r min(exams)`-`r max(exams)+1`. Among those with stage 1 hypertension, `r inline$prevHighRiskS1hDiabetes` of US adults with diabetes and `r inline$prevHighRiskS1hCkd` with CKD had 10-year predicted risk for ASCVD ≥10% or prevalent CVD. In contrast, a much larger proportion of US adults with ≥65 years and stage 1 hypertension had a 10-year predicted risk for ASCVD ≥10% or prevalent CVD: `r inline$prevHighRiskS1hAge65`. Among adults whose 10-year predicted risk for ASCVD was <10%, roughly half of those with diabetes or CKD were not close to the threshold of 10%, whereas over 90% of adults aged ≥65 years had 10-year predicted risk for ASCVD between 5% and 10%.

<!-- These results are not consistent the guideline's claim that a vast majority of adults with stage 1 hypertension and diabetes or CKD have 10-year predicted risk for ASCVD ≥10%. However, the guideline's claim regarding 10-year predicted ASCVD risk among adults with ≥65 years of age is consistent with our findings: `r inline$prevHighRiskAge65` of US adults aged ≥65 years and `r inline$prevHighRiskS1hAge65` of US adults aged ≥65 years with stage 1 hypertension have 10-year predicted risk for ASCVD ≥10% or prevalent CVD. -->

@@

The 2017 ACC/AHA BP guideline suggested that the vast majority of adults with diabetes, CKD, or ≥65 years of age have a 10-year predicted risk for ASCVD ≥10%. Prior studies suggest adults with diabetes or CKD have high risk for CVD. [@coresh2004evidence; @chronic2010association; @grundy1999diabetes] Moreover, adults with diabetes or CKD tend to be older, age is both a strong risk factor for incident ASCVD and a highly influential predictor in the Pooled Cohort risk equations.[@lakatta2002age; @pencina2019quantifying] However, the current study estimates suggest that a high proportion of US adults with diabetes or CKD do not have a high 10-year predicted risk for ASCVD, especially those with stage 1 hypertension.

Previous studies have shown that the use of 10-year predicted risk to guide the decision to initiate antihypertensive medication is critical for US adults with stage 1 hypertension in the general population and for those aged ≥60 years.[@colantonio20182017; @jaeger2019cardiovascular] In an analysis of adults aged ≥60 years, those with stage 1 hypertension recommended versus not recommended to initiate antihypertensive medication by the 2017 ACC/AHA BP guideline were roughly 5 times more likely to experience stroke or coronary heart disease over 12.2 years of follow-up, and 87.7% of the adults with stage 1 hypertension recommended to initiate treatment by the 2017 ACC/AHA BP guideline had a 10-year predicted risk for ASCVD ≥10%. However, the mean age of adults in this group was 70.2 years, whereas the estimated mean (95% CI) age of US adults, 40 to 79 years of age, with stage 1 hypertension in the current analysis was `r inline$meanAgeS1h` years. The younger age of adults in the US compared to adults in observational studies with stage 1 hypertension likely explains the difference in the distribution of 10-year predicted risk for ASCVD found in the current study versus previous studies.

While the current study found that 10-year predicted risk for ASCVD is low among US adults with diabetes or CKD in younger age groups, their lifetime CVD risk may be high.[@lloyd2006prediction; @hippisley2010derivation] For younger adults with diabetes or CKD, antihypertensive medication may provide substantial reduction in lifetime risk for ASCVD and prevention of complications associated with diabetes or CKD. In the current analysis, adults with stage 1 hypertension and diabetes were expected to have 10-year predicted ASCVD risk ≥10% roughly 10 years before their counterparts without diabetes. Patient-provider discussions should clarify the difference in 10-year and lifetime CVD risk and allow for early initiation of antihypertensive medication based on patient preference. Early initialization of treatment may reduce lifetime CVD burden and reverse trends in worsening BP control rates.(CITE Muntner JAMA)

@@

This study has several limitations. First, NHANES participants completed only one visit and guidelines recommend using the mean BP aggregated over 2 or more visits. Second, the response rate for NHANES has declined form 1999-2000 to 2017-2018. The effect of this decline on the current study is unclear. Third, the use of predicted ASCVD risk rather than observed ASCVD events may have over- or under-estimated ASCVD risk in subgroups where the pooled cohort risk equations are not well-calibrated. The current study also has a number of strengths. First, NHANES data are publicly available and representative of the US population when coupled with the NHANES survey design. Second, a collection of open-source software geared to enhance the transparency and reproducibility of scientific findings were leveraged to make the current analysis entirely reproducible and publicly available (see first author's GitHub repository: < _Link not yet active so we won't be scooped_ >). A point of novelty is that anyone with internet access may download this repository of code and reproduce the current manuscript as-is or with different initial parameters, e.g. using data from four NHANES cycles rather than three or modifying exclusion criteria. When different parameters are used, results in the manuscript will dynamically update. A detailed set of instructions for engaging with the project is provided in the repository.

@@

In conclusion, a majority but not all US adults aged 40 to 79 years with diabetes, CKD or ≥65 years of age years have 10-year predicted risk for ASCVD ≥10%. Among those with stage 1 hypertension, this percentage is lower. Most older US adults with diabetes or CKD will have high risk. For younger adults with diabetes or CKD and 10-year predicted risk for ASCVD <10%, early initiation of antihypertensive medication may be an important step towards lowering lifetime CVD risk. Future studies should assess the cost-to-benefit ratio of early treatment for this population.

>>>>

Byron C. Jaeger^1^, Swati Sakhuja^2^, Shakia T. Hardy^2^, Paul Muntner^2^, and Paul K. Whelton^3^

@@

In November 2017, the American College of Cardiology and the American Heart Association (ACC/AHA) published a guideline for the prevention, detection, evaluation, and management of high blood pressure (BP) in adults.[@whelton20182017] This guideline recommends using both predicted cardiovascular disease (CVD) risk and BP levels to guide the initiation of antihypertensive medication.  All adults with systolic BP (SBP) ≥140 mm Hg or diastolic BP (DBP) ≥90 mm Hg, stage 2 hypertension in the guideline, are recommended to initiate antihypertensive medication. Additionally, adults with SBP between 130 and 139 mm Hg and/or DBP between 80 and 89 mm Hg, stage 1 hypertension in the guideline, who have high CVD risk are recommended to initiate antihypertensive medication. In the guideline, high CVD risk is defined by a history of CVD, a 10-year predicted risk for atherosclerotic CVD (ASCVD) ≥10%, the presence of diabetes mellitus or chronic kidney disease (CKD), and age ≥65 years.

The 2017 ACC/AHA guideline recommends estimating 10-year risk for ASCVD in all adults with hypertension, including those with diabetes, CKD or ≥65 years of age. However, the guideline states that the vast majority of adults with diabetes, CKD, or ≥65 years of age can be assumed to have a 10-year ASCVD risk ≥10%. The purpose of the current analysis was to estimate the proportion of US adults with diabetes, CKD, or ≥65 years of age, that have high ASCVD risk defined by a 10-year predicted ASCVD risk ≥10% or a history of CVD.  A secondary objective was to estimate the proportion with high ASCVD risk among adults with diabetes, CKD or ≥65 years of age among those and stage 1 hypertension as the 2017 ACC/AHA BP guideline recommends initiation of antihypertensive medication for all of these adults. To accomplish these goals, we analyzed data from `r as.english(length(exams))` cycles of the US National Health and Nutrition Examination Survey (NHANES).

@@

The current analysis was restricted to adults aged 40 to 79 years of age who complete the NHANES interview and examination (n = `r n_age_40_to_79`). Participants <40 or >79 years of age were not included because the Pooled Cohort risk equations are not recommended to be used in these age ranges.[@goff20142013] Participants who did not have three SBP and DBP measurements (n = `r n_bp_too_low`) and those who were missing information on age, race, sex, total and high-density lipoprotein cholesterol, smoking status, diabetes, or CKD status (n = `r n_missing_pcr`) were excluded. After these exclusions, over the `r as.english(length(exams))` NHANES cycles, a total of `r n_final` survey participants were included in the analysis (`r refer_to('fig_include_exclude')`).

@@

Data were collected during an in-home interview and a study visit completed at a mobile examination center. Standardized questionnaires were used to assess participants’ age, sex, race/ethnicity, smoking habits, medical history and use of antihypertensive medication, oral glucose lowering medication and insulin. Medical history included questions about whether the participant had been told by a doctor or other health professional that they have had a heart attack, coronary heart disease stroke, or heart failure. Blood and urine samples were collected during the medical examination. Of relevance to the current analysis, serum creatinine, serum glucose and glycated hemoglobin (HbA1c) were measured. Diabetes was defined by fasting serum glucose ≥`r gluc_cutpoint_fasted` mg/dL, non-fasting glucose ≥`r gluc_cutpoint_fed` mg/dL, HbA1c ≥`r hba1c_cutpoint`%, or self-reported use of insulin or oral glucose lowering medication. Estimated glomerular filtration rate was calculated using the Chronic Kidney Disease Epidemiology Collaboration equation.[@levey2009new] Urinary albumin and creatinine levels were measured and used to calculate the albumin-to-creatinine ratio (ACR). CKD was defined by an estimated glomerular filtration rate <`r egfr_cutpoint` ml/min/1.73m^2^ or an ACR ≥`r acr_cutpoint` mg/dL. Ten-year predicted risk for ASCVD was calculated using the Pooled Cohort risk equations for participants without a history of CVD.[@goff20142013] High ASCVD risk was defined as a history of CVD or a 10-year predicted ASCVD risk ≥10%.

@@

Participants not taking antihypertensive medication were grouped into four non-overlapping categories based on the 2017 ACC/AHA BP guideline: Normal BP (SBP <120 mm Hg and DBP <80 mm Hg), elevated BP (SBP between 120 and 129 mm Hg and DBP <80 mm Hg), stage 1 hypertension (SBP between 130 and 139 mm Hg and/or DBP between 80 and 89 mm Hg with SBP <140 mm Hg and DBP <90 mm Hg), stage 2 hypertension (SBP ≥140 mm Hg or DBP ≥90 mm Hg). Participants taking antihypertensive medication were placed in a fifth category.

@@

Analyses were conducted for the overall population and among participants with diabetes, CKD, ≥65 years of age, and for those with any of these three conditions. Participant characteristics were summarized as mean with their standard error and percentage for continuous and categorical variables, respectively. The percentage of US adults in each of the five BP categories was computed. The median 10-year predicted risk among participants without a history of CVD was estimated overall and among BP categories in addition to the proportion of participants at high ASCVD risk. To assess the extent to which participants with a 10-year predicted ASCVD risk <10% were close to the 10% threshold, the proportion of participants in this subgroup with predicted risk of 0% to <2.5%, 2.5% to <5.0%, 5.0% to <7.5%, and 7.5% to <10% was estimated. The probability of having high ASCVD risk was estimated for each year of age from 40 to 79 years using logistic regression. The above analyses were repeated among participants with stage 1 hypertension.

@@

# R version string with fancy date
R_string <- glue::glue("R version {version$major}.{version$minor}")

date_string <- with(version, paste(year, month, day, sep = '/')) %>% 
  as.POSIXct() %>% 
  format("%B %d, %Y")

R_string_fancy <- glue::glue(
  "{R_string} (released {date_string})"
)

NHANES sampling weights, which were calculated as the inverse probability of being selected for the survey, were used in all calculations to obtain US nationally representative estimates. The survey design of NHANES was also taken into account. P-values were two-sided. Data analysis was conducted using `r R_string_fancy` along with a collection of open-source software packages (e.g., drake, dflow, officedown, and others) geared to enhance the transparency and reproducibility of our findings.[@cite_R; @cite_drake; @cite_tidyverse; @cite_table.glue] The first author's GitHub repository (< _Link not yet active so we won't be scooped_ >) provides code to reproduce the current manuscript as-is or with different initial parameters including exclusion criteria, variable definitions, and number of NHANES exams to pool. A detailed set of instructions for engaging with the project is provided in the repository's ReadMe file.

@@

Among US adults who were 40 to 79 years of age in `r min(exams)`-`r max(exams)+1`, the estimated prevalence (95% confidence interval [CI]) of diabetes and CKD was `r inline$prevDiabetesOverall` and `r inline$prevCkdOverall`, respectively, and `r inline$prevAge65Overall` were estimated to be ≥65 years of age (`r refer_to('tab_characteristics')`). An estimated `r inline$prevS1hOverall` of US adults who were 40 to 79 years of age had stage 1 hypertension (`r refer_to('tab_bpdist')`). Among those with diabetes, CKD, and age ≥65 years, the estimated prevalence (95% CI) of stage 1 hypertension was `r inline$prevS1hDiabetes`, `r inline$prevS1hCkd`, and `r inline$prevS1hAge65`, respectively. Characteristics of US adults 40 to 79 years of age with stage 1 hypertension, overall, and among those with diabetes, CKD and age ≥65 years are presented in Table S1

@@

Among US adults without a history of CVD, the estimated median (25th, 75th percentiles) 10-year predicted risk for ASCVD was `r inline$medianPcrOverall` in the overall population and `r inline$medianPcrDiabetes`, `r inline$medianPcrCkd`, and `r inline$medianPcrAge65` among those with diabetes, CKD, and age ≥65 years, respectively (`r refer_to('tab_risk_overall')`; top panel). Among US adults with stage 1 hypertension without a history of CVD, the estimated median (25th, 75th percentiles) 10-year predicted risk for ASCVD was `r inline$medianPcrS1hOverall`. Within this subgroup of adults with stage 1 hypertension, those with diabetes, CKD, and age ≥65 years had median (25th, 75th percentiles) predicted risks of of `r inline$medianPcrS1hDiabetes`, `r inline$medianPcrS1hCkd`, and `r inline$medianPcrS1hAge65` respectively. Among all US adults with stage 1 hypertension, an estimated `r inline$prevHighRiskS1hDiabetes` of those with diabetes, `r inline$prevHighRiskS1hCkd` of those with CKD and `r inline$prevHighRiskS1hAge65` who were ≥65 years of age had high ASCVD risk defined by a 10-year predicted risk for ASCVD ≥10% or a history of CVD (`r refer_to('tab_risk_overall')`; bottom panel).

@@

Among US adults who were not at high risk for ASCVD, an estimated `r inline$propLowRiskOverall` of US adults had 10-year predicted ASCVD risk <5% (`r refer_to('fig_hist_ovrl')`). Among those with diabetes, CKD and age ≥65 years, an estimated `r inline$propLowRiskDiabetes`, `r inline$propLowRiskCkd`, and `r inline$propLowRiskAge65` had a 10-year predicted ASCVD risk <5%, respectively. Among US adults with stage 1 hypertension who were not at high risk for ASCVD, an estimated `r inline$propLowRiskS1hDiabetes`, `r inline$propLowRiskS1hCkd`, and `r inline$propLowRiskS1hAge65` of those with diabetes, CKD, and ≥65 years of age had a 10-year predicted ASCVD risk <5%, respectively (`r refer_to('fig_hist_stg1')`).

@@

The estimated probability of having high ASCVD risk increased with older age and exceeded 50% at `r inline$ageHighRiskOvrlNoComorb` years for US adults without diabetes or CKD compared with `r inline$ageHighRiskOvrlDiabetes` and `r inline$ageHighRiskOvrlCkd` years for US adults with diabetes and CKD, respectively (`r refer_to('fig_risk_ovrl')`). Among US adults with stage 1 hypertension, the age at which the estimated probability of having high ASCVD risk exceeded 50% was `r inline$ageHighRiskS1hNoComorb`, `r inline$ageHighRiskS1hDiabetes`, and `r inline$ageHighRiskS1hCkd` years for US adults without diabetes or CKD, with diabetes, and with CKD, respectively (`r refer_to('fig_risk_stg1')`). The minimum age where the probability of high ASCVD risk exceeded 50% was not determined for adults ≥65 years of age as the probability exceeded 50% at all ages above 65 years.

@@

In the current study, a majority of US adults with diabetes, CKD or age ≥65 years had a high risk for ASCVD, defined by a 10-year predicted ASCVD risk ≥10% or history of CVD. However, a substantial proportion of US adults with stage 1 hypertension and diabetes, CKD, or age ≥65 years did not have high ASCVD risk. Among all US adults who were not at high risk for ASCVD, approximately half of those with diabetes or CKD had a 10-year predicted ASCVD risk <5%. In contrast, over 80% of adults aged ≥65 years had 10-year predicted risk for ASCVD between 5% and 10%. The probability of having high risk was age-dependent with over 50% of those with diabetes who were 55 years of age and older and with CKD who were age 59 years of age and older having high ASCVD risk.

@@

Previous studies have shown that the use of predicted ASCVD risk in addition to BP can direct antihypertensive medication to adults likely to receive the largest risk reduction benefit with treatment.[@colantonio20182017; @jaeger2019cardiovascular] In an analysis of the Reasons for Geographic and Racial Differences in Stroke (REGARDS) study, those with stage 1 hypertension recommended versus not recommended to initiate antihypertensive medication by the 2017 ACC/AHA BP guideline were roughly 6 times more likely to experience a CVD event over 8 years of follow-up. Although a substantial proportion of US adults with stage 1 hypertension and diabetes, CKD and age ≥ 65 years of age did not have a high ASCVD risk, they were more likely to have high ASCVD risk when compared to the overall US population with stage 1 hypertension. This suggests adults with stage 1 hypertension and diabetes, CKD or age ≥ 65 years of age may obtain greater risk reduction versus the overall population by initiating antihypertensive medication.

@@

It has been suggested that the vast majority of adults with diabetes, CKD, or ≥65 years of age have a 10-year predicted risk for ASCVD ≥10%. Diabetes or CKD are each associated with an increased risk for ASCVD events.[@coresh2004evidence; @chronic2010association; @grundy1999diabetes] Moreover, in the current study, the mean age was 4 to 6 years older for US adults with diabetes and CKD versus the overall US population.  Age is a strong risk factor for incident ASCVD and a strong contributor to 10-year predicted ASCVD risk in the Pooled Cohort risk equations.[@lakatta2002age; @pencina2019quantifying] However, the current study estimates suggest that a high proportion of US adults with diabetes or CKD do not have a high 10-year predicted risk for ASCVD, especially those with stage 1 hypertension. Future studies should assess the absolute CVD risk reduction for this population with antihypertensive medication treatment.

@@

Although a majority of older adults with diabetes and CKD had high ASCVD risk while the majority of younger adults did not have high ASCVD risk.  However, most young adults with diabetes and CKD have a high lifetime CVD risk.[@lloyd2006prediction; @hippisley2010derivation] Prior studies have found that cumulative exposure to high BP is associated with increased CVD risk.[@allen2014blood] Therefore, for younger adults with diabetes or CKD, antihypertensive medication may provide substantial reduction in ASCVD across their life course. Patient-provider discussions, including discussions of 10-year and lifetime risk for CVD, and patient preference should be used to guide the decision to initiate antihypertensive medication.

The current study has a number of strengths. The design of NHANES allows its results to be weighted to provide results that are representative of the US population. Additionally, NHANES data are collected following a rigorous protocol by trained study staff.  BP was measured three times following a standardized protocol. However, the results of this study should be considered in the context of known and potential limitations. NHANES participants completed only one visit and guidelines recommend using the mean BP averaged over 2 or more visits. The use of predicted ASCVD risk rather than observed ASCVD events may have over- or under-estimated ASCVD risk in subgroups where the Pooled Cohort risk equations are not well-calibrated.

In conclusion, a majority of US adults aged 40 to 79 years with diabetes, CKD or ≥65 years of age had 10-year predicted risk for ASCVD ≥10%. However, a lower percentage of with stage 1 hypertension and diabetes, CKD or age ≥65 years of age had 10-year predicted risk for ASCVD ≥10%. While most older US adults with diabetes or CKD have high risk, a substantial proportion of younger adults with diabetes or CKD have a 10-year predicted risk for ASCVD <10%.  While prevention of hypertension should be a primary goal, the early initiation of antihypertensive medication may be an important step towards lowering lifetime CVD risk.
